Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
joining two paragraphs
luis comments up

This empirical study exhibits proof that changes applied in the codebase to fix
vulnerabilities affect code maintainability. Especially, for refactorings that
address \emph{Broken Authentication and Session Management} issues, \emph{Memory
Leaks} and \emph{Denial-of-Service} attacks. There are already several tools that
suggest security improvements using static analysis, dynamic analysis, and even
artificial intelligence. With this study, we intend to highlight the need for tools
to predict the impact of patches on maintainability~\cite{4724577} and documentation
to help developers adopt security best practices~\cite{6311252, 7927935, MESQUIDA201519}.

@@

% \Luis{A primeira threat que falas é que os resultados podem nao generalizar
% para software fechado. Eu acho que deviamos ser mais diretos.}\Sof{Diretos como?}

@@

% \Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
% fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

@@

% \Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
% Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
% diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

% \Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

% \Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

>>>>

This empirical study exhibits proof that changes applied in the codebase to fix
vulnerabilities affect code maintainability. Especially, for refactorings that
address \emph{Broken Authentication and Session Management} issues, \emph{Memory
Leaks} and \emph{Denial-of-Service} attacks. With this study, we intend to highlight the need for tools
to predict the impact of patches on maintainability~\cite{4724577} and documentation
to help developers adopt security best practices~\cite{6311252, 7927935, MESQUIDA201519}.

@@

\Luis{A primeira threat que falas é que os resultados podem nao generalizar
para software fechado. Eu acho que deviamos ser mais diretos.}\Sof{Diretos como?}

@@

\Luis{pode ser uma cena só minha mas acho que fica melhor em vez de comecar
fraseds com "And," usar outros conetores tipo "Besides," "In addition,", etc. œ}

@@

\Luis{eu nao acho que usar 10 guidelines proposed by the Software Improvement
Group (SIG) seja algo que nos esteja a diferenciar. Acho que o a prinicpal
diferenca é que estamos a estudar maintainability issues noutro contexto.}

@@

\Luis{ tambem fizemos analise por linguagem, nesta ultima citacao deviamos falar sobre isso tb.}

@@

\Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}
